---
title: "College and University Revenue by Jurisdiction"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    navbar:
     - { title: "Back", href: "https://rshiny.csccloud.ca", align: Right }
    vertical_layout: scroll
    theme: simplex
    logo: logo2.png

---

```{r setup, include=FALSE}

#setwd("U:/3. Visualizations/01 Live Visualizations/interprovincial")

library(tidyr)
library(plyr)
library(dplyr)
library(stringr)
library(plotly) # devtools::install_github('ropensci/plotly')
library(ggplot2) # devtools::install_github('hadley/ggplot2')
library(flexdashboard) # devtools::install_github('rstudio/flexdashboard')
library(ggthemes)
library(leaflet)
library(scales)
#library(rgdal)
library(htmltools)
library(bsplus)

#Read data from tidy and alignment script
fiuc <- read.csv("fiuc.csv", header=TRUE, col.names = c("NA","NA","REVENUE","Ref_Date", "Fund", "Value","Category","GEO"))[ ,3:8]
fincol <- read.csv("fincol.csv", header=TRUE, col.names = c("NA","NA","REVENUE","Ref_Date", "Fund", "Value","Category","GEO"))[ ,3:8]
#pop <- read.csv("pop.csv",header=TRUE)[3:5] # unused; for provincial population integration, eventually

enrol <- read.csv("enrol.csv", header=TRUE)[,3:8]
enrolcol <- enrol[enrol$TYPE=="College",]
enrol <- enrol[enrol$TYPE=="University",]


# testing code:
# input <- NULL
# input$immigra <- unique(enrol$IMMIGRA)
# input$GEO2 <- unique(fiuc$GEO)
# input$cat <- unique(fiuc$Category)
# input$fund <- unique(fiuc$Fund)
# input$status <- unique(enrol$STATUS)
# enrolr<-enrol
# enrolr <- filter(enrolr,enrolr$STATUS==input$status[1] , enrolr$IMMIGRA == input$immigra[1])
# enrolr <- group_by(enrolr, Ref_Date, GEO2)
# enrolRaw <- summarise_each(enrolr,funs(sum),-TYPE,-STATUS,-IMMIGRA)

#Reactive global filters and aggregation of data depending on inputs
# commented code in this section is draft material to fix saskatchewan
enrol.r <-  reactive({
  enrolr<-enrol
  enrolr %>%
  filter(STATUS==input$status,IMMIGRA == input$immigra) %>%
  group_by(Ref_Date, GEO2) %>%
  summarise_each(funs(sum),-TYPE,-STATUS,-IMMIGRA) -> enrolRaw
  
     
     interpolateyears <- c("2004/2005","2005/2006","2006/2007","2007/2008","2008/2009","2009/2010")
     dropyears <- c("2005/2006","2006/2007","2007/2008","2008/2009")
     startVal <- filter(enrolRaw,GEO2 == "SK",Ref_Date == "2004/2005")$Value
     endVal <- filter(enrolRaw,GEO2 == "SK",Ref_Date == "2009/2010")$Value
     step = (endVal-startVal )/5
     #make a series of just 5 years for SK; interpolated
     enrolRaw$ValueSK <- NA
     for(i in 1:6){
       enrolRaw[enrolRaw$Ref_Date == interpolateyears[i] & enrolRaw$GEO2=="SK",]$ValueSK <- startVal+((i-1)*step)
     }
     #Null out offending years
     enrolRaw[enrolRaw$GEO2=="SK" & enrolRaw$Ref_Date %in% dropyears,]$Value <- NA
     enrolRaw
  })

enrolcol.r = reactive({
  enrolcolr<-enrolcol
  enrolcolr %>%
  filter(STATUS==input$statuscol,IMMIGRA == input$immigracol) %>%
  group_by(Ref_Date, GEO2) %>%
  summarise_each(funs(sum),-TYPE,-STATUS,-IMMIGRA)
  })

fiuc.r = reactive({
  fiucr <- fiuc
  fiucr <- fiucr[fiucr$GEO %in% input$prov & fiucr$Category %in% input$cat & fiucr$Fund %in% input$fund,]
  })

fincol.r = reactive({
  fincolr <- fincol
  fincolr <- fincol[fincolr$GEO %in% input$provcol & fincolr$Category %in% input$catcol & fincolr$Fund %in% input$fundcol,]
  })

#Graph Legend Controls
v <- list(
  font = list(
    family = "sans-serif",
    size = 10,
    color = "#000"),
  bgcolor = "#BFFFFFFF",
  bordercolor = "#FFFFFF",
  borderwidth = 2,
  x = 0,
  y = -.3,orientation = 'h')


superdollars <- function(x, ... ,pref=""){
  postf <- NULL
  Base <- x
  if (x>=1e12){
    Base <- x/1e12
    postf <- "T"
  }
  else if (x>=1e9){
    Base <- x/1e9
    postf <- "B"
  }
  else if (x>=1e6){
    Base <- x/1e6
    postf <- "M"
  }  
  else if (x>=1e3){
    Base <- x/1e3
    postf <- "k"
  }
  output <- paste(pref,round(Base,2),postf,sep="") 
  output
}

```


About
=====================================  

Row 
-------------------------------------

### Purpose


This interactive web application visualizes system-level revenues end expenditures at post-secondary institutions. This simplifies and visualizes the data reported by colleges and universities in the *Financial Information of Universities and Colleges survey*, an annual reporting tool managed by CAUBO, and the *FINCOL curvey, a similar data collection tool for colleges that is managed by Statistics Canada.

This tool can help: 

* Compare different types of sector revenue across provinces; and,
* Explore trends in revenue overall and per student. 



This tool can help: 

* Compare different types of sector revenue across provinces; and,
* Explore trends in revenue overall and per student. 


Row 
-------------------------------------

### Content

This tool contains the following sections (available in the main menu above):

* A summary of Univeristy Revenues; and,
* A comparative summary of College Revenues.

Future updates will include institutional expenditures, and comparison of individual institutions. 

Row 
-------------------------------------

### Tool Functions 

This tool summarizes and compares institutional revenue. This includes the following features: 

* View revenue per student, per person, or sector totals;
* Filter data by immigration status or registration status;
* Explore different types of revenue; and,
* Compare provinces and trends over time.

Row 
-------------------------------------

### Notes

Due to a reporting issue, student counts are incorrectly reported in Saskatchewan from 2005 through 2008, showing lower total enrolment counts than expected.

The application is built with the [Shiny](http://shiny.rstudio.com) framework for the [R programming language](https://www.r-project.org/). The application layout is produced with the [flexdashboard](http://rstudio.github.io/flexdashboard/index.html) package, and the charts and maps use [Plotly](http://plot.ly) and [ggplot2](http://ggplot2.org/), all accessed through their corresponding R packages.  

The data is entirely open, and sourced from __StatCan__, including the following sets:

* [Table 477-0058: Financial information of universities and degree-granting colleges, revenues by type of fund](http://www20.statcan.gc.ca/tables-tableaux/cansim/csv/04770058-eng.zip)
* [Table 477-0060: Financial information of community colleges and vocational schools, revenues by type of fund](http://www20.statcan.gc.ca/tables-tableaux/cansim/csv/04770060-eng.zip)
* [Table 477-0019: Postsecondary enrolments, by registration status, Pan-Canadian Standard Classification of Education (PCSCE), Classification of Instructional Programs, Primary Grouping (CIP_PG), sex and student status](http://www20.statcan.gc.ca/tables-tableaux/cansim/csv/04770019-eng.zip)

### Contact

* Does this tool meet your needs? 
* Do the use cases resonate with you?
* Are there other use cases or features you think would be helpful?

Should you encounter any issues with this tool, please contact the Funding Policy and System Planning Unit at MAESD: http://www.infogo.gov.on.ca/infogo/#orgProfile/5640/en 

University Revenues
======================================================================

Inputs {.sidebar data-width=300}
-------------------------------------

### Select and filter data

__Measure to be used__
```{r}

#Define inputs
#Add per capita, per 18-24 and store in denominator
#Could add download link for visible data

#Per student/population
# radioButtons('per', label = NULL, choiceValues = c("Total","Enrolment","Population"),choiceNames = c("Sector total ","Funding per-student (FTE Enrolment)","Funding per person (Population)"), selected = "Enrolment")

radioButtons('per', label = NULL, choiceValues = c("Total","Enrolment"),choiceNames = c("Sector total ","Funding per-student (FTE Enrolment)"), selected = "Enrolment")

#Could add fund as input
#Could add download link for visible data

```



__Enrolment measure (if selected above)__
```{r}
selectInput('immigra', label = 'Immigration status', choices = unique(enrol$IMMIGRA), selected = "Canadian students")
selectInput('status', label = 'Registration status', choices = unique(enrol$STATUS), selected = "Full-time student")
```

__Select provinces to display__
```{r}
checkboxGroupInput('prov', label = NULL, choices = unique(fiuc$GEO),selected=unique(fiuc$GEO))
```

__Select revenue categories to display__
```{r}
checkboxGroupInput('cat', label = NULL, choices = unique(fiuc$Category),unique(fiuc$Category))
```

__Select funds to display__
```{r}
checkboxGroupInput('fund', label = NULL, choices = unique(fiuc$Fund),unique(fiuc$Fund))


```

__Select year to investigate__
```{r}
selectInput('year', label = NULL, choices = unique(fiuc$Ref_Date), selected = "2014/2015")

#Download data
output$downloadData <- downloadHandler(
 filename = function() {
      paste("data-", Sys.Date(), ".csv", sep="")
    },
 content = function(file) {
      write.csv(enrolcol.r, file)
    }
  )
  
downloadLink('downloadData', label = 'Download Data')
```

Row 
-----------------------------------------------------------------------

### University Revenues Over Time

```{r}

#Revenue by category with ggplotly
output$revtime <- renderPlotly({
  fiuc.t <- fiuc.r()
  fiuc.t <- fiuc.t %>%
  group_by(GEO, Ref_Date) %>%
  summarise_each(funs(sum),-REVENUE,-Fund,-Category)
  
  enrol.t <- enrol.r()
  
  #Merge Denominator
    if(input$per=="Enrolment"){
    fiuc.t <- merge(fiuc.t, enrol.t, by.x = c('GEO','Ref_Date'), by.y = c("GEO2",'Ref_Date'), all.x=TRUE)
    fiuc.t$amountSK <- 1000*fiuc.t$Value.x/fiuc.t$ValueSK
  } else if(input$per=="Population"){
    fiuc.t <- merge(fiuc.t, pop, by.x = c('GEO','Ref_Date'), by.y = c("GEO2",'Ref_Date'), all.x=TRUE)
  } else if(input$per=="Total"){
    fiuc.t$Value.y<-as.numeric(1)
    colnames(fiuc.t)[3]<-"Value.x"
  }

  
  fiuc.t$Ref_Date <- as.numeric(substr(fiuc.t$Ref_Date,1,4))
  fiuc.t$amount  <- 1000*fiuc.t$Value.x/fiuc.t$Value.y

  
  #p1a <- ggplot(fiuc.t, aes(x=Ref_Date,y=amount, colour=GEO)) + 
    #geom_line() +
    #geom_point(alpha=.4) +
    #scale_y_continuous(labels = scales::dollar) +
    #theme_minimal(base_size = 11) + scale_colour_hue(name="Province") +
    #ylab('Revenue ($K)') + xlab('Year') +
    #theme(legend.title=element_blank(),legend.key = element_rect(fill = "transparent", colour = "transparent"))
  
  #p1a<-plot_ly(data=fiuc.t, x=fiuc.t$Ref_Date,y=fiuc.t$amount,type='scatter', mode='lines',color=~GEO, tickprefix = "$", ticksuffix="K")
  #g <- ggplotly(p1a, source = 'source',hoverinfo = 'text',text = paste('Amount:', amount))

  
  

  p1a <- plot_ly(fiuc.t, 
                hoverinfo = 'text', 
                text = ~paste('Province: ', GEO,'</br>', 
                               '</br>Revenue: ', 
                               mapply(x=((
                                            ifelse(is.na(fiuc.t$amount),fiuc.t$amountSK,fiuc.t$amount))),
                                      FUN=superdollars,
                                      pref="$"),
                               '</br>year: ', Ref_Date,
                               sep=""
                               )) %>%
                add_trace(x=fiuc.t$Ref_Date,
                          y=fiuc.t$amount,
                          type='scatter', 
                          mode='lines+markers',
                          color=~GEO
                          ) %>%
                layout(yaxis = list(title="Revenue", 
                                    tickprefix = "$", 
                                    ticksuffix=""),
                       xaxis = list(title="Year"))
  
  if(input$per=="Enrolment"){
  p1a <- p1a  %>% add_trace(x=fiuc.t$Ref_Date,
                          y=fiuc.t$amountSK,
                          type='scatter', 
                          mode='lines+markers',
                          color=~GEO,
                          line=list(dash='dot',
                                    color=rgb(.7,.7,.7)
                                    ),
                          showlegend = FALSE
                          )}
  
  
  p1a
  
})  

plotlyOutput('revtime')

```

Row
-----------------------------------------------------------------------

### University Revenues by Category 

```{r}

#Filter and aggregate data
output$revcat <- renderPlotly({

  fiuc.c <- fiuc.r()
  fiuc.c <- fiuc.c[fiuc.c$Ref_Date==input$year,]

  fiuc.c <- fiuc.c %>%
  group_by(GEO, Category) %>%
  summarise_each(funs(sum),-REVENUE,-Fund, -Ref_Date)
  
  enrol.c <- enrol.r()
  enrol.c <- enrol.c[enrol.c$Ref_Date==input$year,]
  
  #Merge denominator
  if(input$per=="Enrolment"){
    fiuc.c <- merge(fiuc.c, enrol.c, by.x = 'GEO', by.y = "GEO2", all.x=TRUE)
  } else if(input$per=="Population"){
    #insert population merge
  } else if(input$per=="Total"){
    fiuc.c$Value.y<-1
    colnames(fiuc.c)[3]<-"Value.x"
  }
   
  fiuc.c$amount  <- fiuc.c$Value.x/fiuc.c$Value.y*1000
  fiuc.c <- ddply(fiuc.c, .(GEO), transform, pos = cumsum(amount) - (0.5 * amount))

  #Plot
  #p1a <- ggplot(fiuc.c, aes(x=GEO,y=amount, fill=Category)) + 
    #geom_bar(stat="identity", alpha = .8) +
    #geom_text(data=fiuc.c,aes(label = dollar(round(amount,digits=2)), y= pos), size = 3) +
    #scale_y_continuous(labels = scales::dollar) +
    #theme_minimal(base_size = 11) + scale_colour_hue(name="Province") +
    #ylab('Revenue ($K)') + xlab('Category') +
    #theme(legend.title=element_blank(),legend.key = element_rect(fill = "transparent", colour = "transparent"))

  #p1a <- ggplotly(p1a, source = 'source') %>%
  #layout(legend = v,hoverinfo="text")
  
  p1a <- plot_ly(fiuc.c,
                hoverinfo = 'text', 
                text = ~paste('Category: ', Category, '</br>', 
                               '</br>Revenue: ', 
                                mapply(x=fiuc.c$amount,
                                      FUN=superdollars,
                                      pref="$"),
                               '</br>Year: ', input$year,
                               sep=""
                               )) %>%
    add_trace(x=fiuc.c$GEO,
              y=fiuc.c$amount,type='bar', 
              color=~Category
              ) %>%
    layout(yaxis = list(title=paste(input$year,"  revenue"), 
                        tickprefix = "$", 
                        ticksuffix=""),
           xaxis = list(title="Province"), 
           barmode='stack',
           legend = list(orientation = 'h'))
  #data labels
  p1a
  
})  

plotlyOutput('revcat')
```

### University Revenues by Fund

```{r}

#Filter and aggregate data
output$revfund <- renderPlotly({

  fiuc.f <- fiuc.r()
  fiuc.f <- fiuc.f[fiuc.f$Ref_Date==input$year,]

  fiuc.f <- fiuc.f %>%
  group_by(GEO, Fund) %>%
  summarise_each(funs(sum),-REVENUE,-Category,-Ref_Date)
  
  enrol.f <- enrol.r()
  enrol.f <- enrol.f[enrol.f$Ref_Date==input$year,]
  
  #Merge denominator
  if(input$per=="Enrolment"){
    fiuc.f <- merge(fiuc.f, enrol.f, by.x = 'GEO', by.y = "GEO2", all.x=TRUE)
  } else if(input$per=="Population"){
    #insert population merge
  } else if(input$per=="Total"){
    fiuc.f$Value.y<-1
    colnames(fiuc.f)[3]<-"Value.x"
  }
   
  fiuc.f$amount  <- 1000*fiuc.f$Value.x/fiuc.f$Value.y
  fiuc.f <- ddply(fiuc.f, .(GEO), transform, pos = cumsum(amount) - (0.5 * amount))
  
  #Plot
  #p1a <- ggplot(fiuc.f, aes(x=GEO,y=amount, fill=Fund)) + 
    #geom_bar(stat="identity", alpha = .8) +
    #geom_text(data=fiuc.f,aes(label = dollar(round(amount,digits=2)), y= pos), size = 3) +
    #scale_y_continuous(labels = scales::dollar) +
    #theme_minimal(base_size = 11) + scale_colour_hue(name="Province") +
    #ylab('Revenue ($K)') + xlab('Fund') +
    #theme(legend.title=element_blank(),legend.key = element_rect(fill = "transparent", colour = "transparent"))

  #p1a <- ggplotly(p1a, source = 'source') %>%
  #layout(legend = v,hoverinfo="text")
  
  p1a <- plot_ly(fiuc.f,
                 hoverinfo = 'text', 
                 text = ~paste('Fund: ', Fund,  '</br>', 
                             '</br>Revenue: ', 
                             mapply(x=fiuc.f$amount,
                                      FUN=superdollars,
                                      pref="$"),
                             '</br>Year: ', input$year,
                             sep=""
                 )) %>%
    add_trace(x=fiuc.f$GEO,
              y=fiuc.f$amount,
              type='bar', 
              color=~Fund
              ) %>%
    layout(yaxis = list(title=paste(input$year,"  revenue"), 
                        tickprefix = "$", 
                        ticksuffix=""),
           xaxis = list(title="Province"), 
           barmode='stack',
           legend = list(orientation = 'h'))
  #data labels
  p1a
  
})  

plotlyOutput('revfund')
```

College Revenues
======================================================================

Inputs {.sidebar data-width=300}
-------------------------------------

### Select and filter data

__Measure to be used__
```{r}

#Define inputs
#Add per capita, per 18-24 and store in denominator
#Could add download link for visible data

#Per student/population
#radioButtons('percol', label = NULL, choiceValues = c("Total","Enrolment","Population"), choiceNames = c("Sector total ","Funding per-student (FTE Enrolment)","Funding per person (Population)"),selected = "Enrolment")

radioButtons('percol', label = NULL, choiceValues = c("Total","Enrolment"), choiceNames = c("Sector total ","Funding per-student (FTE Enrolment)"),selected = "Enrolment")


```

__Enrolment measure (if selected above)__
```{r}
selectInput('immigracol', label = 'Immigration status', choices = unique(enrolcol$IMMIGRA), selected = "Canadian students")
selectInput('statuscol', label = 'Registration status', choices = unique(enrolcol$STATUS), selected = "Full-time student")
```

__Select provinces to display__
```{r}
checkboxGroupInput('provcol', label = NULL, choices = unique(fincol$GEO),selected=unique(fincol$GEO))
```

__Select revenue categories to display__
```{r}
checkboxGroupInput('catcol', label = NULL, choices = unique(fincol$Category),unique(fincol$Category))
```

__Select funds to display__
```{r}
checkboxGroupInput('fundcol', label =  NULL, choices = unique(fincol$Fund),unique(fincol$Fund))
```

__Select year for detail view__
```{r}
selectInput('yearcol', label = NULL, choices = unique(fincol$Ref_Date), selected = "2014/2015")
```

Row 
-----------------------------------------------------------------------

### College Revenues Over Time

```{r}

#Revenue by category with ggplotly
output$revtimecol <- renderPlotly({
  fincol.t <- fincol.r()
  fincol.t <- fincol.t %>%
  group_by(GEO, Ref_Date) %>%
  summarise_each(funs(sum),-REVENUE,-Fund,-Category)
  
  enrolcol.t <- enrolcol.r()
  
  #Merge Denominator
    if(input$percol=="Enrolment"){
    fincol.t <- merge(fincol.t, enrolcol.t, by.x = c('GEO','Ref_Date'), by.y = c("GEO2",'Ref_Date'), all.x=TRUE)
  } else if(input$percol=="Population"){
    #insert population merge
  } else if(input$percol=="Total"){
    fincol.t$Value.y<-as.numeric(1)
    colnames(fincol.t)[3]<-"Value.x"
  }

  fincol.t$Ref_Date <- as.numeric(substr(fincol.t$Ref_Date,1,4))
  fincol.t$amount  <- fincol.t$Value.x/fincol.t$Value.y
  
  # p1a <- ggplot(fincol.t, aes(x=Ref_Date,y=amount, colour=GEO)) + 
  #   geom_line() +
  #   geom_point(alpha=.4) +
  #   scale_y_continuous(labels = scales::dollar) +
  #   theme_minimal(base_size = 11) + scale_colour_hue(name="Province") +
  #   ylab('Revenue ($K)') + xlab('Year') +
  #   theme(legend.title=element_blank(),legend.key = element_rect(fill = "transparent", colour = "transparent"))
  #   
  # p1a
  # g <- ggplotly(p1a, source = 'source')
  
  p1a <- plot_ly(fincol.t,
                hoverinfo = 'text', 
                text = ~paste('Province: ', GEO, '</br>', 
                               '</br>Revenue: ',
                              # mapply(x=fincol.t$amount,
                              #         FUN=superdollars,
                              #         pref="$"), 
                              superdollars(1000*fincol.t$amount,"$"),
                               '</br>year: ', Ref_Date,
                               sep=""
                               )) %>%
                add_trace(x=fincol.t$Ref_Date,
                          y=fincol.t$amount*1000,
                          type='scatter',
                          mode='lines+markers',
                          color=~GEO
                          ) %>%
                layout(yaxis = list(title="revenue",
                                    tickprefix = "$"
                                    ),
                       xaxis = list(title="Year"))
  p1a
  
})  

plotlyOutput('revtimecol')

```

Row
-----------------------------------------------------------------------

### College Revenues by Category

```{r}

#Filter and aggregate data
output$revcatcol <- renderPlotly({

  fincol.c <- fincol.r()
  fincol.c <- fincol.c[fincol.c$Ref_Date==input$yearcol,]

  fincol.c <- fincol.c %>%
  group_by(GEO, Category) %>%
  summarise_each(funs(sum),-REVENUE,-Fund, -Ref_Date)
  
  enrolcol.c <- enrolcol.r()
  enrolcol.c <- enrolcol.c[enrolcol.c$Ref_Date==input$yearcol,]
  
  #Merge denominator
  if(input$percol=="Enrolment"){
    fincol.c <- merge(fincol.c, enrolcol.c, by.x = 'GEO', by.y = "GEO2", all.x=TRUE)
  } else if(input$percol=="Population"){
    #insert population merge
  } else if(input$percol=="Total"){
    fincol.c$Value.y<-1
    colnames(fincol.c)[3]<-"Value.x"
  }
   
  fincol.c$amount  <- fincol.c$Value.x/fincol.c$Value.y*1000
  fincol.c <- ddply(fincol.c, .(GEO), transform, pos = cumsum(amount) - (0.5 * amount))

  #Plot
  # p1a <- ggplot(fincol.c, aes(x=GEO,y=amount, fill=Category)) + 
  #   geom_bar(stat="identity", alpha = .8) +
  #   geom_text(data=fincol.c,aes(label = dollar(round(amount,digits=2)), y= pos), size = 3) +
  #   scale_y_continuous(labels = scales::dollar) +
  #   theme_minimal(base_size = 11) + scale_colour_hue(name="Province") +
  #   ylab('Revenue ($K)') + xlab('Category') +
  #   theme(legend.title=element_blank(),legend.key = element_rect(fill = "transparent", colour = "transparent"))
  # 
  # p1a <- ggplotly(p1a, source = 'source') %>%
  # layout(legend = v)
  
  
  
   p1a <- plot_ly(fincol.c,
                hoverinfo = 'text', 
                text = ~paste('Category: ', Category, '</br>', 
                               '</br>Revenue: ', 
                              mapply(x=fincol.c$amount,
                                      FUN=superdollars,
                                      pref="$"),
                               '</br>Year: ', input$year,
                               sep=""
                               )) %>%
    add_trace(x=fincol.c$GEO,
              y=fincol.c$amount,type='bar', 
              color=~Category
              ) %>%
    layout(yaxis = list(title=paste(input$year,"  revenue"), 
                        tickprefix = "$", 
                        ticksuffix=""),
           xaxis = list(title="Province"), 
           barmode='stack',
           legend = list(orientation = 'h'))

  p1a 
  
  
})  

plotlyOutput('revcatcol')
```

### College Revenues by Fund

```{r}

#Filter and aggregate data
output$revfundcol <- renderPlotly({

  fincol.f <- fincol.r()
  fincol.f <- fincol.f[fincol.f$Ref_Date==input$yearcol,]
  
  fincol.f <- fincol.f %>%
  group_by(GEO, Fund) %>%
  summarise_each(funs(sum),-REVENUE,-Category,-Ref_Date)
  
  enrolcol.f <- enrolcol.r()
  enrolcol.f <- enrolcol.f[enrolcol.f$Ref_Date==input$yearcol,]
  
  #Merge denominator
  if(input$percol=="Enrolment"){
    fincol.f <- merge(fincol.f, enrolcol.f, by.x = 'GEO', by.y = "GEO2", all.x=TRUE)
  } else if(input$percol=="Population"){
    #insert population merge
  } else if(input$percol=="Total"){
    fincol.f$Value.y<-1
    colnames(fincol.f)[3]<-"Value.x"
  }
   
  fincol.f$amount  <- fincol.f$Value.x/fincol.f$Value.y*1000
  fincol.f <- ddply(fincol.f, .(GEO), transform, pos = cumsum(amount) - (0.5 * amount))
  
  # #Plot
  # p1a <- ggplot(fincol.f, aes(x=GEO,y=amount, fill=Fund)) + 
  #   geom_bar(stat="identity", alpha = .8) +
  #   geom_text(data=fincol.f,aes(label = dollar(round(amount,digits=2)), y= pos), size = 3) +
  #   scale_y_continuous(labels = scales::dollar) +
  #   theme_minimal(base_size = 11) + scale_colour_hue(name="Province") +
  #   ylab('Revenue ($K)') + xlab('Fund') +
  #   theme(legend.title=element_blank(),legend.key = element_rect(fill = "transparent", colour = "transparent"))
  # 
  # p1a <- ggplotly(p1a, source = 'source') %>%
  # layout(legend = v)
  
  
  
    p1a <- plot_ly(fincol.f,
                 hoverinfo = 'text', 
                 text = ~paste('Fund: ', Fund, '</br>',  
                             '</br>Revenue: ', 
                             mapply(x=fincol.f$amount,
                                      FUN=superdollars,
                                      pref="$"),
                             '</br>Year: ', input$year,
                             sep=""
                 )) %>%
    add_trace(x=fincol.f$GEO,
              y=fincol.f$amount,
              type='bar', 
              color=~Fund
              ) %>%
    layout(yaxis = list(title=paste(input$year,"  revenue"), 
                        tickprefix = "$", 
                        ticksuffix=""),
           xaxis = list(title="Province"), 
           barmode='stack',
           legend = list(orientation = 'h'))
  #data labels
  p1a
  
})  

plotlyOutput('revfundcol')
```


<style>

/*basic formatting*/

 #sidebar.section.sidebar {
     background-color: rgba(51, 122, 183, 0.4);
     font-family: "Open Sans", "Helvetica Neue", Helvetica, Arial, sans-serif !important;
 }
 body {
     background: rgba(0, 0, 0, 0.015);
 }
 .section.sidebar {
     background-color: #f8f8f8;
 }
 .value-box {
     color: inherit;
 }
 .bg-primary {
     background-color: rgba(51, 122, 183, 0.4);
 }
 .nav-tabs-custom > .nav-tabs > li.active {
     border-top-color: rgba(51, 122, 183, 0.4);
 }
 .navbar-inverse {
     background-color: #691bad;
     border-color: #691bad;
 }

 .navbar-inverse .navbar-brand:hover,
 .navbar-inverse .navbar-brand:focus {
     color: #ffffff;
     background-color: none;
 }
 .navbar-inverse .navbar-text {
     color: #ffffff;
 }
 .navbar-inverse .navbar-nav > li > a {
     color: #ffffff;
 }
 .navbar-inverse .navbar-nav > .active > a,
 .navbar-inverse .navbar-nav > .active > a:hover,
 .navbar-inverse .navbar-nav > .active > a:focus {
     color: #ffffff;
     background-color: rgba(157, 25, 190, 0.8);
 }

 .navbar-inverse .navbar-nav > .active > a:hover {
     text-decoration: underline;
 }

/* Minor adjustments to improve visual hierarchy and spacing*/ 

.chart-title{
     font-size: 14px;
     font-weight: bold;
     padding: 7px 10px 7px;
}

.chart-wrapper .chart-stage {
     padding: 10px 10px 5px 15px;
}

li:before {
    margin-left: -4px;
}

li:{
     padding-left: 8px;
}

p:{
    margin: 5px 0 9px 0;
}

.container-fluid {
     padding: 21px 15px 5px 25px;
}

.navbar-logo {
     margin-top: -3px;
     margin-right: 20px;
}

.navbar-inverse .navbar-brand {
    color: #ffffff;
    font-weight: bold;
}


/* Adjust workspace to accommodate larger header */

.section.sidebar{
    margin-top: 30px;
    background: #f9f9f9; /* For browsers that do not support gradients */
    background: -webkit-linear-gradient(left top, #f9f9f9, #ededed); /* For Safari 5.1 to 6.0 */
    background: -o-linear-gradient(bottom right, #f9f9f9, #ededed); /* For Opera 11.1 to 12.0 */
    background: -moz-linear-gradient(bottom right, #f9f9f9, #ededed); /* For Firefox 3.6 to 15 */
    background: linear-gradient(to bottom right, #f9f9f9, #ededed); /* Standard syntax */
}

/* Next section must be customized for each viz to reflect chart titles */

div#section-graphs, div#section-enrolment-vs-sma-targets, div#section-percent-difference, div#section-university-revenues-over-time, div#section-college-revenues-over-time, div#section-university-revenues-over-time{
   margin-top: 30px;  
}
div#section-purpose {
   margin-top: 38px;
   max-width: 1200px;
   margin-left: 15%;
   margin-right: 15%;
}

div#section-content, div#section-context, div#section-tool-functions  {
   max-width: 1200px;
   margin-left: 15%;
   margin-right: 15%;
}

div#section-notes  {
   max-width: 600px;
   margin-left: 15%;
}

div#section-contact  {
   max-width: 600px;
   margin-right: 15%;
}

/* reorganize inputs a little */

input#test17, input#test18, input#test19, input#test20, input#test21 {
     width: 80%;
}

.shiny-input-container label {
    /*float: left;*/
    padding: 9px 8px 0px 9px;
    font-size: 13px;
    
}

.radio label {
    min-width:198px;
    margin-left:20px;
}

.btn {
    float:left;
    margin-right:10px;
    background-color:#9e7abf;
}

.btn-default{
  background-color:#9e7abf;
  background-image:inherit;
  border-color:rgba#9e7abf;
  border:1px solid rgb(185, 185, 185);
}
.btn-default:hover{
  background-color:#8059a3;
  background-image:inherit;
  border-color:#8059a3;
}

h4{
  margin-top:25px;
}

.woot{
    background-color: #9e7abf;
    border: none;
    color: white;
    padding: 10px;
    text-align: center;
    text-decoration: none;
    display: inline-block;
    font-size: 14px;
    width:100%;
    margin-bottom:16px;
}

.woot:hover{
    background-color: #8059a3;
    text-decoration: none;
}

.checkbox{
    margin: 0 0 0 20px;
}

/* add fancy radio buttons */
.radio input[type="radio"]{
  margin-left:-23px;
  margin-top:0px;
}

    input[type='radio']:after {
        width: 20px;
        height: 20px;
        border-radius: 20px;
        margin-top:-1px;
        margin-left:-2px;
        position: relative;
        background-color: #d1d3d1;
        content: '';
        display: inline-block;
        visibility: visible;
        border: 2px solid white;
    }

    input[type='radio']:checked:after {
        width: 20px;
        height: 20px;
        border-radius: 20px;
        margin-top:-1px;
        margin-left:-2px;
        position: relative;
        background-color: #9e7abf;
        content: '';
        display: inline-block;
        visibility: visible;
        border: 2px solid white;
    }

.radio{
  margin-bottom:0px;
}

/* download button */

a#downloadData{
    background-color: #9e7abf;
    border: none;
    color: white;
    padding: 10px;
    text-align: center;
    text-decoration: none;
    display: inline-block;
    font-size: 14px;
    width:100%;
}
a#downloadData:hover{
    background-color: #8059a3;
    text-decoration: none;
}

/* Reset */
.reset{
    background-color: #9e7abf;
    border: none;
    color: white;
    padding: 10px;
    text-align: center;
    text-decoration: none;
    display: inline-block;
    font-size: 14px;
    width:100%;
}
.reset:hover{
    background-color: #8059a3;
    text-decoration: none;
}

</style>
